Index measures for oak decline severity using phenotypic descriptors

### 2020-01-27 manuscript/manuscript.Rmd
added surveyors to acknowledgements

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest,
      PDI_rf_tune_params,
      DAI_rf_tune_params,
      analysis_suitable_data,
      site_corrected_analysis_suitable_data,
      remission_PDI_group_ttest,
      remission_DAI_group_ttest,
      DAI_descriptor_importance)
```

@@

We would like to thank the Forest Research TSU for collecting the phenotypic data presented in this article especially Liz Richardson and Mark Oram for coordinating surveying.
This work was supported by Woodland Heritage and the Future Proofing Plant Health (FPPH) Oak Resilience project.

>>>>

```{r loadData, include = FALSE}
loadd(site_rf_margin,
      site_rf_post_correction_margin,
      PDI_status_ttest,
      DAI_groups_ttest,
      PDI_rf_tune_params,
      DAI_rf_tune_params,
      analysis_suitable_data,
      site_corrected_analysis_suitable_data,
      remission_PDI_group_ttest,
      remission_DAI_group_ttest,
      DAI_descriptor_importance,
      surveyors_names)
```

@@

We would like to thank the Forest Research TSU for collecting the phenotypic data presented in this article. Thanks to Liz Richardson and Mark Oram for coordinating surveying and the surveyors: `r str_c(surveyors_names,collapse = ', ')`.
This work was supported by Woodland Heritage and the Future Proofing Plant Health (FPPH) Oak Resilience project.
